---
title: "Length Based Indicators (LBI)"
author: ""
date: "`r Sys.Date()`"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_float: yes
  pdf_document:
    number_sections: yes
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r, warning=FALSE, message=FALSE, echo=FALSE,include=FALSE}
library(kableExtra)
library(tidyverse)

# require (rJava)
# .jinit()
# .jcall('java.lang.System','S','getProperty','java.version')
# [1] "1.8.0_211"
#devtools::install_github('davidgohel/ReporteRsjars')
# devtools::install_github('davidgohel/ReporteRs')
library(LBSPR) 
library(reshape2)
library(ggplot2) 
library(tidyr)
library(ReporteRs) 
source("https://raw.githubusercontent.com/ices-tools-dev/LBIndicator_shiny/master/utilities.R") 
source("utilities_vpaz.R") 
```


Loading catch at length per year:


```{r,warning=FALSE, message=FALSE,}
freq <- read.csv("data_freq.csv", stringsAsFactors = FALSE)
head(freq)
tail(freq)
```

Loading mean weights-at-length per year (a=0.009476898 and b=3.018329):


```{r,warning=FALSE, message=FALSE,}
wal <- read.csv("data_wei2.csv", stringsAsFactors = FALSE)
head(wal)
tail(wal)
```


Length distributions over time must be unimodal, then maybe the length frequency data needs to be grouped.


```{r, message=FALSE}
bin_plot(freq, 1, "cm")
```

Based on the previous plot we have decided to apply the method for Binwidth parameter
 (width of length bins) equal to 1.
 
 
## Reference model


```{r,warning=FALSE}
lb_tableSH(freq, 1, "cm", linf=48.9, lmat=26, mk_ratio=1.41,wal)
lb_plot(freq, 1, "cm", linf=48.9, lmat=26, mk_ratio=1.41,wal)
```


## Sensitivity analysis of $L_{\inf}$

### Overestimation

#### $L_{\inf} \times 1.1$

```{r,warning=FALSE}
lb_tableSH(freq, 1, "cm", linf=48.9*1.1, lmat=26, mk_ratio=1.41,wal)
```

### Underestimation 

#### $L_{\inf} \times 0.9$

```{r,warning=FALSE}
lb_tableSH(freq, 1, "cm", linf=48.9*0.9, lmat=26, mk_ratio=1.41,wal)
```


## Sensitivity analysis of $M/K$

### Overestimation

#### $M/K \times 1.1$

```{r,warning=FALSE}
lb_tableSH(freq, 1, "cm", linf=48.9, lmat=26, mk_ratio=1.41*1.1,wal)
```


### Underestimation 

#### $M/K \times 0.9$

```{r,warning=FALSE}
lb_tableSH(freq, 1, "cm", linf=48.9, lmat=26, mk_ratio=1.41*0.9,wal)
```


## Sensitivity analysis of $L_{mat}$

### Overestimation

#### $L_{mat} \times 1.1$

```{r,warning=FALSE}
lb_tableSH(freq, 1, "cm", linf=48.9, lmat=26*1.1, mk_ratio=1.41,wal)
```



### Underestimation 

#### $L_{mat} \times 0.9$

```{r,warning=FALSE}
lb_tableSH(freq, 1, "cm", linf=48.9, lmat=26*0.9, mk_ratio=1.41,wal)
```

