---
title: "Mean length-based mortality estimators (MLZ)"
author: ""
date: "`r Sys.Date()`"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_float: yes
  pdf_document:
    number_sections: yes
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Preparing data

### Read data and format it

The effort time-series is derived from the ratio of the catch and a LPUE series of Portugal. 

```{r,message=FALSE,include=FALSE}


library(fishmethods)
library(dplyr)
library(lattice)
library(data.table)
library(reshape2)

# Modification for discrete (annual) reproduction
source('gedamke.hoenig_BFGS_discrete.r')
# THoG model
source('mleneffort.r')
# YPR estimator
source('ypr_ml.r')

# Function to calculate mean lengths
neph_Lbar <- function(input, Lc){
  sub <- subset(input, Length >= Lc & !(value==0))
  sub <- data.table(sub)
  fin <- sub[, list(
    mlen = sum(value * Length) / sum(value),
    ss_bins = length(value),
    ss = 1
  ),
  by = list(Year)]
  fin$Year <- as.numeric(fin$Year)
  out <- fin
}
```


```{r,message=FALSE}
input_lenfreq <- read.csv('data_freq.csv')
input_effort <- read.csv('effort.csv')
colnames(input_lenfreq)[1] <- "Length"

name <- "Solea"
sex <- "Both"
K <- 0.22
Linf <- 48.9
max_age <- 15 

input_melt <- melt(input_lenfreq, id.vars="Length", variable.name="Year")
input_melt$Year <- as.numeric(substr(input_melt$Year, 2, 5))

head(input_lenfreq)
tail(input_lenfreq)

input_effort
```

### Histograms and definition of length of full selectivity ($L_c$)


```{r}
stockname <- paste(name, sex)

par(mfrow=c(1, 1))
input_tot <- rowSums(input_lenfreq[, -1])
input_lengths <- input_lenfreq[,1]

Lc <- input_lengths[which.max(input_tot)] ; Lc
barplot(input_tot, names.arg=input_lengths, 
        main=paste(stockname, "Length Frequency Distribution \nPeak=", Lc))
```



### Calculate annual mean lengths of animals of lengths larger than $L_c$ 

```{r}
ml_gh <- neph_Lbar(input=input_melt, Lc=Lc)
ml_gh
```

## Then model

Note that the initial value of $q$ have been fixed as the value estimate using M fixed in Then model.

### Reference model

```{r}
ml_thog <- left_join(input_effort, 
                     ml_gh, 
                     by = "Year")
ml_thog$ss_bins[is.na(ml_thog$ss_bins)] <- 0
ml_thog$ss[is.na(ml_thog$ss)] <- 0
```

```{r}
# Guess for q
q0=0.15/mean(ml_thog$effort)
###
max_age <- 15
mlen_effort(year = ml_thog$Year,
            mlen = ml_thog$mlen,
            effort = ml_thog$effort, 
            ss = ml_thog$ss,
            K = K,
            Linf = Linf, 
            Lc = Lc, 
            n_cohort = 1,
            n_age = max_age, 
            init_effort = rep(ml_thog$effort[1], max_age),
            stq = c(q0),
            stM = c(.3))
```




### Model fixing M

```{r}
mlen_effort(year = ml_thog$Year,
            mlen = ml_thog$mlen,
            effort = ml_thog$effort, 
            ss = ml_thog$ss,
            K = K,
            Linf = Linf, 
            Lc = Lc, 
            n_cohort = 1,
            n_age = max_age, 
            init_effort = rep(ml_thog$effort[1], max_age),
            stq = c(q0),
            stM = c(.31), est.M = F)


```



### Sensitivity analysis of $L_{\inf}$

#### Overestimation

##### $L_{\inf} \times 1.1$


```{r}
max_age <- 15
mlen_effort(year = ml_thog$Year,
            mlen = ml_thog$mlen,
            effort = ml_thog$effort, 
            ss = ml_thog$ss,
            K = K,
            Linf = Linf*1.1, 
            Lc = Lc, 
            n_cohort = 1,
            n_age = max_age, 
            init_effort = rep(ml_thog$effort[1], max_age),
            stq = c(q0),
            stM = c(.3))
```




#### Underestimation 

###### $L_{\inf} \times 0.9$


```{r}
max_age <- 15
mlen_effort(year = ml_thog$Year,
            mlen = ml_thog$mlen,
            effort = ml_thog$effort, 
            ss = ml_thog$ss,
            K = K,
            Linf = Linf*0.9, 
            Lc = Lc, 
            n_cohort = 1,
            n_age = max_age, 
            init_effort = rep(ml_thog$effort[1], max_age),
            stq = c(q0),
            stM = c(.3))
```


### Sensitivity analysis of $K$

#### Overestimation

##### $K \times 1.1$


```{r}
max_age <- 15
mlen_effort(year = ml_thog$Year,
            mlen = ml_thog$mlen,
            effort = ml_thog$effort, 
            ss = ml_thog$ss,
            K = K*1.1,
            Linf = Linf, 
            Lc = Lc, 
            n_cohort = 1,
            n_age = max_age, 
            init_effort = rep(ml_thog$effort[1], max_age),
            stq = c(q0),
            stM = c(.3))
```



#### Underestimation 

###### $K \times 0.9$


```{r}
max_age <- 15
mlen_effort(year = ml_thog$Year,
            mlen = ml_thog$mlen,
            effort = ml_thog$effort, 
            ss = ml_thog$ss,
            K = K*0.9,
            Linf = Linf, 
            Lc = Lc, 
            n_cohort = 1,
            n_age = max_age, 
            init_effort = rep(ml_thog$effort[1], max_age),
            stq = c(q0),
            stM = c(.3))
```



### Sensitivity analysis of $q$ initial value

#### Overestimation

##### $q \times 1.1$


```{r}
max_age <- 15
mlen_effort(year = ml_thog$Year,
            mlen = ml_thog$mlen,
            effort = ml_thog$effort, 
            ss = ml_thog$ss,
            K = K,
            Linf = Linf, 
            Lc = Lc, 
            n_cohort = 1,
            n_age = max_age, 
            init_effort = rep(ml_thog$effort[1], max_age),
            stq = c(q0*1.1),
            stM = c(.3))
```




#### Underestimation 

###### $q \times 0.9$


```{r}
max_age <- 15
mlen_effort(year = ml_thog$Year,
            mlen = ml_thog$mlen,
            effort = ml_thog$effort, 
            ss = ml_thog$ss,
            K = K,
            Linf = Linf, 
            Lc = Lc, 
            n_cohort = 1,
            n_age = max_age, 
            init_effort = rep(ml_thog$effort[1], max_age),
            stq = c(q0*0.9),
            stM = c(.3))
```


### Sensitivity analysis of $max_{age}$


#### Overestimation

##### $max_{age} \times 1.1$


```{r}
max_age <- 15*1.1
mlen_effort(year = ml_thog$Year,
            mlen = ml_thog$mlen,
            effort = ml_thog$effort, 
            ss = ml_thog$ss,
            K = K,
            Linf = Linf, 
            Lc = Lc, 
            n_cohort = 1,
            n_age = max_age, 
            init_effort = rep(ml_thog$effort[1], max_age),
            stq = c(q0),
            stM = c(.3))
```




#### Underestimation 

###### $max_{age} \times 0.9$


```{r}
max_age <- 15*0.9
mlen_effort(year = ml_thog$Year,
            mlen = ml_thog$mlen,
            effort = ml_thog$effort, 
            ss = ml_thog$ss,
            K = K,
            Linf = Linf, 
            Lc = Lc, 
            n_cohort = 1,
            n_age = max_age, 
            init_effort = rep(ml_thog$effort[1], max_age),
            stq = c(q0),
            stM = c(.3))
```


### Sensitivity analysis of $L_c$


#### Overestimation

##### $L_c \times 1.05$


```{r}
max_age <- 15
mlen_effort(year = ml_thog$Year,
            mlen = ml_thog$mlen,
            effort = ml_thog$effort, 
            ss = ml_thog$ss,
            K = K,
            Linf = Linf, 
            Lc = Lc*1.05, 
            n_cohort = 1,
            n_age = max_age, 
            init_effort = rep(ml_thog$effort[1], max_age),
            stq = c(q0),
            stM = c(.3))
```




#### Underestimation 

###### $L_c \times 0.95$


```{r}
max_age <- 15
mlen_effort(year = ml_thog$Year,
            mlen = ml_thog$mlen,
            effort = ml_thog$effort, 
            ss = ml_thog$ss,
            K = K,
            Linf = Linf, 
            Lc = Lc*0.95, 
            n_cohort = 1,
            n_age = max_age, 
            init_effort = rep(ml_thog$effort[1], max_age),
            stq = c(q0),
            stM = c(.3))
```
