---
title: "Length Based Spawning Potential Ratio (LB-SPR)"
author: ""
date: "`r Sys.Date()`"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_float: yes
  pdf_document:
    number_sections: yes
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```




## Reference model

```{r,warning=FALSE}
library(LBSPR) 
```


```{r,message=FALSE}
Solea1Pars <- new("LB_pars")
Solea1Pars@Linf <- 48.9
Solea1Pars@L50 <- 26
Solea1Pars@L95 <- 27.5
Solea1Pars@MK <- 1.41 
Solea1Pars@L_units <- "cm"
```

```{r}
SoleaLenFreq1 <- new("LB_lengths", LB_pars=Solea1Pars, file="data_freq.csv", dataType="freq", header=TRUE)
SoleaLenFreq1@L_units <- Solea1Pars@L_units
plotSize(SoleaLenFreq1)
```


```{r}
Fit1 <- LBSPRfit(Solea1Pars, SoleaLenFreq1, verbose = FALSE)
plotEsts(Fit1)
```

We can access to the estimates directly:

```{r}
Fit1@SPR
```

Smoother values:

```{r}
data.frame(Fit1@Ests)
```



## Sensitivity analysis of $L_{inf}$

### Overestimation

#### $L_{inf}\times 1.1$.

```{r,message=FALSE}
Solea2Pars <- new("LB_pars")
Solea2Pars@Linf <- 48.9*1.1
Solea2Pars@L50 <- 26
Solea2Pars@L95 <- 27.5
Solea2Pars@MK <- 1.41
Solea2Pars@L_units <- "cm"
```

```{r}
SoleaLenFreq2 <- new("LB_lengths", LB_pars=Solea2Pars, file="data_freq.csv", dataType="freq", header=TRUE)
SoleaLenFreq2@L_units <- Solea2Pars@L_units


```


```{r}
Fit2 <- LBSPRfit(Solea2Pars, SoleaLenFreq2, verbose = FALSE)
plotEsts(Fit2)
```

We can access to the estimates directly:
  
```{r}
Fit2@SPR
```

Smoother values:
  
```{r}
data.frame(Fit2@Ests)
```


### Underestimation

#### $L_{inf} \times 0.90$.

```{r,message=FALSE}
Solea3Pars <- new("LB_pars")
Solea3Pars@Linf <- 48.9*0.90
Solea3Pars@L50 <- 26
Solea3Pars@L95 <- 27.5
Solea3Pars@MK <- 1.41
Solea3Pars@L_units <- "cm"
```

```{r}
SoleaLenFreq3 <- new("LB_lengths", LB_pars=Solea3Pars, file="data_freq.csv", dataType="freq", header=TRUE)
SoleaLenFreq3@L_units <- Solea3Pars@L_units


```


```{r}
Fit3 <- LBSPRfit(Solea3Pars, SoleaLenFreq3, verbose = FALSE)
plotEsts(Fit3)
```

We can access to the estimates directly:
  
```{r}
Fit3@SPR
```

Smoother values:
  
```{r}
data.frame(Fit3@Ests)
```


## Sensitivity analysis of $M/K$

### Overestimation

#### $M/K\times 1.1$.

```{r,message=FALSE}
Solea4Pars <- new("LB_pars")
Solea4Pars@Linf <- 48.9
Solea4Pars@L50 <- 26
Solea4Pars@L95 <- 27.5
Solea4Pars@MK <- 1.41*1.1
Solea4Pars@L_units <- "cm"
```

```{r}
SoleaLenFreq4 <- new("LB_lengths", LB_pars=Solea4Pars, file="data_freq.csv", dataType="freq", header=TRUE)
SoleaLenFreq4@L_units <- Solea4Pars@L_units


```


```{r}
Fit4 <- LBSPRfit(Solea4Pars, SoleaLenFreq4, verbose = FALSE)
plotEsts(Fit4)
```

We can access to the estimates directly:
  
```{r}
Fit4@SPR
```

Smoother values:
  
```{r}
data.frame(Fit4@Ests)
```

### Underestimation

#### $M/K \times 0.90$.

```{r,message=FALSE}
Solea5Pars <- new("LB_pars")
Solea5Pars@Linf <- 48.9
Solea5Pars@L50 <- 26
Solea5Pars@L95 <- 27.5
Solea5Pars@MK <- 1.41*0.90
Solea5Pars@L_units <- "cm"
```

```{r}
SoleaLenFreq5 <- new("LB_lengths", LB_pars=Solea5Pars, file="data_freq.csv", dataType="freq", header=TRUE)
SoleaLenFreq5@L_units <- Solea5Pars@L_units


```


```{r}
Fit5 <- LBSPRfit(Solea5Pars, SoleaLenFreq5, verbose = FALSE)
plotEsts(Fit5)
```

We can access to the estimates directly:
  
```{r}
Fit5@SPR
```

Smoother values:
  
```{r}
data.frame(Fit5@Ests)
```


## Sensitivity analysis of $L_{50}$ and $L_{95}$ 

### Overestimation

#### $L_{50}\times 1.1$ and $L_{95}\times 1.1$

```{r,message=FALSE}
Solea6Pars <- new("LB_pars")
Solea6Pars@Linf <- 48.9
Solea6Pars@L50 <- 26*1.1
Solea6Pars@L95 <- 27.5*1.1
Solea6Pars@MK <- 1.41
Solea6Pars@L_units <- "cm"
```

```{r}
SoleaLenFreq6 <- new("LB_lengths", LB_pars=Solea6Pars, file="data_freq.csv", dataType="freq", header=TRUE)
SoleaLenFreq6@L_units <- Solea6Pars@L_units


```


```{r}
Fit6 <- LBSPRfit(Solea6Pars, SoleaLenFreq6, verbose = FALSE)
plotEsts(Fit6)
```

We can access to the estimates directly:
  
```{r}
Fit6@SPR
```

Smoother values:
  
```{r}
data.frame(Fit6@Ests)
```

### Underestimation

#### $L_{50}\times 0.9$ and $L_{95}\times 0.9$

```{r,message=FALSE}
Solea7Pars <- new("LB_pars")
Solea7Pars@Linf <- 48.9
Solea7Pars@L50 <- 26*0.90
Solea7Pars@L95 <- 27.5*0.90
Solea7Pars@MK <- 1.41
Solea7Pars@L_units <- "cm"
```

```{r}
SoleaLenFreq7 <- new("LB_lengths", LB_pars=Solea7Pars, file="data_freq.csv", dataType="freq", header=TRUE)
SoleaLenFreq7@L_units <- Solea7Pars@L_units


```


```{r}
Fit7 <- LBSPRfit(Solea7Pars, SoleaLenFreq7, verbose = FALSE)
plotEsts(Fit7)
```

We can access to the estimates directly:
  
```{r}
Fit7@SPR
```

Smoother values:
  
```{r}
data.frame(Fit7@Ests)
```

